Reanalysis Step 2: Multiple Imputation

### 2025-08-29 reanalysis-2-multiple_imputation_backup_20250829_104333.qmd
enhance mi

```{r mice-run}

@@

@@

>>>>

```{r mice-run}
# Initialize logging
log_file <- init_log("multiple_imputation")
log_message(paste0("Analysis mode: ", analysis_mode))
log_message(paste0("Number of imputations: ", n_imputations))
log_message(paste0("Number of iterations per imputation: ", n_iterations))
log_message(paste0("Number of observations: ", nrow(df_mice)))
log_message(paste0("Variables with missing data: ", sum(colSums(is.na(df_mice)) > 0)))

log_message("Starting MICE imputation process...")
imp_start <- Sys.time()

@@

imp_time <- round(as.numeric(difftime(Sys.time(), imp_start, units = "mins")), 2)
log_message(paste0("MICE imputation completed in ", imp_time, " minutes"))

@@

```{r finalize-log}
# Finalize logging
log_message("Multiple imputation analysis completed successfully")
log_message(paste0("Total imputed datasets created: ", n_imputations))
final_log <- finalize_log(success = TRUE)
```

**Log file location:** `r final_log`
